Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2016-11-05 WSSSPE4_report/WSSSPE4_report.tex
adding survey summary (section 9) and details (appendix E), content from Lorraine

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Survey responses \label{sec:survey}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\note{Lorraine will write this}

\todo{discuss survey responses; maybe put detailed responses in an appendix}

@@

%
\todo{feel free to add stuff here}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Attendee survey \label{sec:survey}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\note{from Lorraine}

All participants present on the last day of the meeting, September 14, 2016, were asked to complete the online survey administered through Qualtrics\footnote{\url{https://www.qualtrics.com}.}.
44 responses were recorded, with one respondent indicating that they took the survey twice.
The survey URL was also later distributed to attendees by email and advertised on twitter for attendees who were not there on the last day to have a chance to respond, and one additional response was recorded after the meeting.
Hence, the total number of unique individuals responding to the survey is likely 44.
The survey contained 9 multiple choice and open-text answer questions.
Text responses have been alphabetize to preserve anonymity.
The survey had a 100\% completion rate.
Appendix~\ref{sec:survey_details} contains the detailed survey results.

In general, the respondents were highly satisfied with the meeting and interested in continuing and participating in WSSSPE activities.
The mix of topics and types of interactions---talks, panels and discussion---was well balanced with several indicating a desire for time for questions and answers following talks as well for discussions in general.
Many respondents indicated that they will remain engaged in WSSSPE working group initiatives.
However, demand for a professional organization encompassing WSSSPE interests was weaker with over half interested in joining and a large percentage willing to consider the idea.
Respondents were grateful for the opportunity to network, explore new collaborations and for travel support to the conference.

The survey results indicate that future WSSSPE conferences should consider the balance of the attendees.
This year's meeting had many first time and early career participants who would have benefited from a review of basic concepts and terminology including what it means for software to be sustainable and the roles of research software engineers.
Additional emphasis and topics to explore would be the inclusion of more case studies, focus on the decision making process in developing and using software, deeper dives into selected topics, tutorials, software training within and outside of STEM, lowering the barriers to implementing best practices in software development, and progress towards executing WSSSPE's vision.

@@

\todo{feel free to add stuff here}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Detailed survey results}  \label{sec:survey_details}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{survey_details}
